\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-05-27 generated/assessments.tex
Lots of simplifications to using multiple Latex files

\citenum{ref-1} & On request.\flagStyle{ } & ``Code is available upon request from the corresponding author'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-2} & ``The datasets used in the current study are available from the corresponding author upon reasonable request and under consideration of the ethical regulations.''\flagStyle{ $\sf R_d$\hskip 3pt{}} & Matlab. Documented overview, but only trivial comments. Assertions in code only relate to UI.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}$\sf C_a$\hskip 3pt{}}\\
\citenum{ref-3} & ``In accordance with Twitter policies of data sharing, data used in the generation of the algorithm for this study will not be made publicly available.''\flagStyle{ } & ``Due to the sensitive and potentially stigmatizing nature of this tool, code used for algorithm generation or implementation on individual Twitter profiles will not be made publicly available.''\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-4} & ``The datasets generated during and/or analyzed during the current study are available from the corresponding author on reasonable request.''\flagStyle{ } & ``This code would be made available upon reasonable request.'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-5} & Nothing available\flagStyle{ } & Nothing available (despite building two voice-based virtual counselors).\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-6} & ``The datasets generated and analyzed during the study are not currently publicly available due to HIPAA compliance agreement but are available from the corresponding author on reasonable request.''\flagStyle{ } & Poor commenting, no documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-7} & ``The dataset generated and analyzed for this study will not be made publicly available due to patient privacy and lack of informed consent to allow sharing of patient data outside of the research team.''\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-8} & ``The datasets generated during and/or analyzed during the current study are not publicly available due to institutional restrictions on data sharing and privacy concerns. However, the data are available from the corresponding author on reasonable request.''\flagStyle{ } & Empty GitHub repository: ``Code coming soon \ldots'' paper says.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf R_{\mbox{\scriptsize c-empty}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-9} & ``The i2b2 data that support the findings of this study are available from i2b2 but restrictions apply to the availability of these data, which require signed safe usage and research-only. Data from UCSF are not available at this time as they have not been legally certified as being De-Identified, however, this process is underway and the data may be available by the time of publication by contacting the authors. Requesters identity as researchers will need to be confirmed, safe usage guarantees will need to be signed, and other restrictions may apply.''\flagStyle{ } & Basic documentation, very little comment.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-10} & ``Not available due to restrictions in the ethical permit, but may be available on request.''\flagStyle{ } & Trivial comments, no documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-11} & ``The data that support the findings of this study are available in a deidentified form from Cleveland Clinic, but restrictions apply to the availability of these data, which were used under Cleveland Clinic data policies for the current study, and so are not publicly available.''\flagStyle{ } & ``We used only free and open-source software'' --- some of which is unspecified.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-12} & ``The i-ROP cohort study data for ROP is not publicly available due to patient privacy restrictions, though potential collaborators are directed to contact the study investigators \ldots''\flagStyle{ } & Not all code on GitHub, minor comments only.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{paper-usesRMarkdown} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code and example runs available in R Markdown.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_3$\hskip 3pt{}}\\
\citenum{ref-14} & Data directly written into program code.\flagStyle{ } & Basic Matlab with routine comments.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{onlyPaperWithChecks} & Data available on Dryad plus publicly available data from the 1000 genomes project. Currently (apparently) for private view.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code available for private view, though some code available with minor comments. Paper describes using two contrasting methods to help confirm correctness, ``As an additional check, I also coded the calculation of D based on a probabilistic approach, using genotype frequencies in each population to calculate the expected frequencies of each possible two-genotype combination (electronic supplementary material, table S1). Essentially identical results were obtained.'' --- but the contrasting method is not available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf S_{{\mbox{\scriptsize otherSE}}}$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-16} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Reasonaby commented code on Dryad, but code is not complete and presumably never checked.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-17} & On request.\flagStyle{ } & R, lightly commented.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ethics-paper} & No data required.\flagStyle{ } & Unrunnable incomplete code fragment.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-19} & Data embedded in PDF.\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-20} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Some comments, some code in Matlab.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-21} & Partial data on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Documented R, including model's manual.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_3$\hskip 3pt{}}\\
\citenum{ref-22} & No data required.\flagStyle{ } & ``We constructed a bioeconomic model for an RSSF [restricted fishing effort small-scale fishery] using game theory'' for which results are discussed, yet no code is available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-23} & Data cited, not all available.\flagStyle{ } & Trivial documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{example-numerical-error} & On Figshare.\flagStyle{ $\sf R_d$\hskip 3pt{}} & On Figshare, large amount of disorganised and undocumented code. Helpful features to make usable for third parties.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-25} & Data on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-26} & Data on various web sites.\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-27} & Data on request.\flagStyle{ } & ``The coding used to train the artificial intelligence model are dependent on annotation, infrastructure, and hardware, so cannot be released.'' (!) Algorithm (not source code) available on request.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-28} & Data on request.\flagStyle{ } & Python scripts can be requested.\flagStyle{ $\sf S_p$\hskip 3pt{}}\\
\citenum{ref-29} & Unspecified location on large website requiring registration.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Has overall documentation but poorly commented Matlab code on GitHub.\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-30} & Available to researchers who meet criteria for access to confidential data.\flagStyle{ } & Despite the paper being a ``deep learning algorithm'' the code is not available.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-31} & Data access conditional on approved study proposal.\flagStyle{ } & Almost completely uncommented Python, but does have a basic setup script.\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-32} & Unspecified locations on several large websites.\flagStyle{ } & Python used and apparently on GitHub, but --- an oversight? --- no code is available.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\

>>>>

\cite{ref-1} & On request.\flagStyle{ } & ``Code is available upon request from the corresponding author'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\cite{ref-2} & ``The datasets used in the current study are available from the corresponding author upon reasonable request and under consideration of the ethical regulations.''\flagStyle{ $\sf R_d$\hskip 3pt{}} & Matlab. Documented overview, but only trivial comments. Assertions in code only relate to UI.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}$\sf C_a$\hskip 3pt{}}\\
\cite{ref-3} & ``In accordance with Twitter policies of data sharing, data used in the generation of the algorithm for this study will not be made publicly available.''\flagStyle{ } & ``Due to the sensitive and potentially stigmatizing nature of this tool, code used for algorithm generation or implementation on individual Twitter profiles will not be made publicly available.''\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-4} & ``The datasets generated during and/or analyzed during the current study are available from the corresponding author on reasonable request.''\flagStyle{ } & ``This code would be made available upon reasonable request.'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\cite{ref-5} & Nothing available\flagStyle{ } & Nothing available (despite building two voice-based virtual counselors).\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-6} & ``The datasets generated and analyzed during the study are not currently publicly available due to HIPAA compliance agreement but are available from the corresponding author on reasonable request.''\flagStyle{ } & Poor commenting, no documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{ref-7} & ``The dataset generated and analyzed for this study will not be made publicly available due to patient privacy and lack of informed consent to allow sharing of patient data outside of the research team.''\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-8} & ``The datasets generated during and/or analyzed during the current study are not publicly available due to institutional restrictions on data sharing and privacy concerns. However, the data are available from the corresponding author on reasonable request.''\flagStyle{ } & Empty GitHub repository: ``Code coming soon \ldots'' paper says.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf R_{\mbox{\scriptsize c-empty}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-9} & ``The i2b2 data that support the findings of this study are available from i2b2 but restrictions apply to the availability of these data, which require signed safe usage and research-only. Data from UCSF are not available at this time as they have not been legally certified as being De-Identified, however, this process is underway and the data may be available by the time of publication by contacting the authors. Requesters identity as researchers will need to be confirmed, safe usage guarantees will need to be signed, and other restrictions may apply.''\flagStyle{ } & Basic documentation, very little comment.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{ref-10} & ``Not available due to restrictions in the ethical permit, but may be available on request.''\flagStyle{ } & Trivial comments, no documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{ref-11} & ``The data that support the findings of this study are available in a deidentified form from Cleveland Clinic, but restrictions apply to the availability of these data, which were used under Cleveland Clinic data policies for the current study, and so are not publicly available.''\flagStyle{ } & ``We used only free and open-source software'' --- some of which is unspecified.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-12} & ``The i-ROP cohort study data for ROP is not publicly available due to patient privacy restrictions, though potential collaborators are directed to contact the study investigators \ldots''\flagStyle{ } & Not all code on GitHub, minor comments only.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{paper-usesRMarkdown} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code and example runs available in R Markdown.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_3$\hskip 3pt{}}\\
\cite{ref-14} & Data directly written into program code.\flagStyle{ } & Basic Matlab with routine comments.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{onlyPaperWithChecks} & Data available on Dryad plus publicly available data from the 1000 genomes project. Currently (apparently) for private view.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code available for private view, though some code available with minor comments. Paper describes using two contrasting methods to help confirm correctness, ``As an additional check, I also coded the calculation of D based on a probabilistic approach, using genotype frequencies in each population to calculate the expected frequencies of each possible two-genotype combination (electronic supplementary material, table S1). Essentially identical results were obtained.'' --- but the contrasting method is not available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf S_{{\mbox{\scriptsize otherSE}}}$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\cite{ref-16} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Reasonaby commented code on Dryad, but code is not complete and presumably never checked.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\cite{ref-17} & On request.\flagStyle{ } & R, lightly commented.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{ethics-paper} & No data required.\flagStyle{ } & Unrunnable incomplete code fragment.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\cite{ref-19} & Data embedded in PDF.\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-20} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Some comments, some code in Matlab.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\cite{ref-21} & Partial data on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Documented R, including model's manual.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_3$\hskip 3pt{}}\\
\cite{ref-22} & No data required.\flagStyle{ } & ``We constructed a bioeconomic model for an RSSF [restricted fishing effort small-scale fishery] using game theory'' for which results are discussed, yet no code is available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-23} & Data cited, not all available.\flagStyle{ } & Trivial documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{example-numerical-error} & On Figshare.\flagStyle{ $\sf R_d$\hskip 3pt{}} & On Figshare, large amount of disorganised and undocumented code. Helpful features to make usable for third parties.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{ref-25} & Data on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-26} & Data on various web sites.\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-27} & Data on request.\flagStyle{ } & ``The coding used to train the artificial intelligence model are dependent on annotation, infrastructure, and hardware, so cannot be released.'' (!) Algorithm (not source code) available on request.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-28} & Data on request.\flagStyle{ } & Python scripts can be requested.\flagStyle{ $\sf S_p$\hskip 3pt{}}\\
\cite{ref-29} & Unspecified location on large website requiring registration.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Has overall documentation but poorly commented Matlab code on GitHub.\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\cite{ref-30} & Available to researchers who meet criteria for access to confidential data.\flagStyle{ } & Despite the paper being a ``deep learning algorithm'' the code is not available.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\cite{ref-31} & Data access conditional on approved study proposal.\flagStyle{ } & Almost completely uncommented Python, but does have a basic setup script.\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\cite{ref-32} & Unspecified locations on several large websites.\flagStyle{ } & Python used and apparently on GitHub, but --- an oversight? --- no code is available.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\

### 2023-05-27 generated/over-fitting-code-section.tex
Lots of simplifications to using multiple Latex files

\subsection{The siren call of over-fitting code}\label{over-fit}
Poor code undermines scientific quality: poor code can generate plausible and possibly misleading results from \emph{any\/} data, including even fictional science. A temptation is that %artificial world \cite{sciences-artificial}, built on adjusting the code's results gets more attention than the theoretical basis of the code's overall faithfulness to the experimental phenomena. 
% wolframscript (if being used) unnecessarily prints the next 2 lines (generated by CellPrint), but they are needed!
\def\imageWidthCalculation{\multiply \imageWidth by 21 \divide \imageWidth by 28}
\def\figureStarDetails{*}

@@

In modeling terms, superficially successful computer programs tend to \emph{over-fit\/} phenomena \cite{over-fit}. Instead of using code to test the models, we tinker with the code adapting it to be closer and closer to our prejudices. The code then apparently confirms our science, since we fitted it to our understanding.

@@

Unfortunately, code in published science \emph{is\/} often over-fitted, and over-fitted in a way that is very hard to scrutinize. For example, in epidemiology (which is considered in section \ref{section-pandemic-modeling}) it is routine to use very complicated, large dynamical models parameterized with numerous social, cultural, health, demographic and geographical data. The parameterization is mixed between data files, data written explicitly into the code, and with conditionals and other structuring in the code to cover special cases. Indeed, many of the programs in the survey used comments to inactivate code, presumably indicating an unfinished tinkering approach to code development.\footnote{Of the \the\countUsesVersionControlRepository\ papers in the pilot survey that reported use of code repositories (covering \input generated/kloc.tex
\totalkLOC\ thousand lines of code --- so this is not a trivial amount of programming effort), \numbertoname{\the\countMissingCode} provided an empty repository with no code at all (effectively commenting out all their code!), and \numbertoname{\the\countCommentedOut} repositories explicitly commented out chunks of workable code. The \numbertoname{\the\countNotCommentedOut} remaining non-trivial repositories with no commented-out code consisted of straightforward, short code files with few comments of any sort.\remembernamevalue{numbernamesexamplefootnote}{\thefootnote}}

>>>>

\subsection{The siren call of over-fitting code}\label{over-fit}
Poor code can generate plausible and possibly misleading results from \emph{any\/} data or theory, including fraudulent science. A temptation is that developing code to get ``good results'' becomes more important than the code's overall faithfulness to the real scientific phenomena, theoretical or empirical. 
% wolframscript (if being used) unnecessarily prints the next 2 lines (generated by CellPrint), but they are needed!
\def\imageWidthCalculation{\multiply \imageWidth by 21 \divide \imageWidth by 28}
\def\figureStarDetails{*}

@@

In conventional modeling terms, successful computer programs are often \emph{over-fitted\/} to phenomena \cite{over-fit}. That is, instead of using code to rigorously challenge, test, and develop our models, we tinker with code adapting it to generate results closer and closer to our prejudices. The code then apparently confirms our science, since we fitted it to our preconceptions but not to the science.

@@

Unfortunately, code in published science \emph{is\/} often over-fitted, and over-fitted in a way that is very hard to scrutinize. For example, in epidemiology (which is considered in section \ref{section-pandemic-modeling}) it is routine to use very complicated, large dynamical models parameterized with numerous social, cultural, health, demographic and geographical data. The parameterization is mixed between data files, data written explicitly into the code, and with conditionals and other structuring in the code to cover special cases. Indeed, many of the programs in the survey used comments to inactivate code, presumably indicating an unfinished tinkering approach to code development.\footnote{Of the \the\countUsesVersionControlRepository\ papers in the pilot survey that reported use of code repositories (covering \input generated/kloc.tex
\totalkLOC\ thousand lines of code --- so this is not a trivial amount of programming effort), \numbertoname{\the\countMissingCode} provided an empty repository with no code at all (effectively commenting out all their code!), and \numbertoname{\the\countCommentedOut} repositories explicitly commented out chunks of workable code. The \numbertoname{\the\countNotCommentedOut} remaining non-trivial repositories with no commented-out code consisted of straightforward, short code files with few comments of any sort.\label{name-example-footnote}}

### 2023-05-27 generated/saved-files.tex
Lots of simplifications to using multiple Latex files

allGitRepos.sh & Shell script generated to download all available 10 GitHub repositories\\
assessments.tex & Main summary table for Supplementary Material\\
clone-date.tex & Running the download script also saves the download dates of GitHub clones\\
constants.tex & Generated \LaTeX\  definitions and constants\\
data-check.html & Convenient list of data sources with DOIs in HTML (enables checking of data just by clicking on HTML links)\\
data.csv & All data from \texttt{data.js} expressed in CSV for convenience\\
example-data.tex & \LaTeX\  example of JSON data\\
flagData.nb & Flags expressed as Mathematica code (facilitates ML or other analysis)\\
legend.tex & Legend for the main assessment table\\
open-doi.sh & Shell script to conveniently open all DOIs\\
page-lengths.tex & Page lengths and totals for Git data, and total pages of papers\\
saved-files.tex & This table of files generated by \texttt{data.js}\\
summary-table.tex & Short summary table\\
supplementary-references.tex & Reference list for Supplementary Material\\

>>>>

allGitRepos.sh & Shell script generated to download all available 10 GitHub repositories\\
assessments.tex & Main summary table for Supplementary Material\\
clone-date.tex & Running the download script also saves the download dates of GitHub clones\\
constants.tex & Generated \LaTeX\  definitions and constants\\
data-check.html & Convenient list of data sources with DOIs in HTML (enables checking of data just by clicking on HTML links)\\
data.csv & All data from \texttt{data.js} expressed in CSV for convenience\\
example-data.tex & \LaTeX\  example of JSON data\\
flagData.nb & Flags expressed as Mathematica code (facilitates ML or other analysis)\\
legend.tex & Legend for the main assessment table\\
open-doi.sh & Shell script to conveniently open all DOIs\\
page-lengths.tex & Page lengths and totals for Git data, and total pages of papers\\
saved-files.tex & This table of files generated by \texttt{data.js}\\
summary-table.tex & Short summary table\\
supplementary-references.bbl & Reference list for Supplementary Material (bbl file)\\
